Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-07-24 manuscript/phylogenetic_signal_manuscript.tex
small catches from Micke

  We found that the composition of plant families in a network
  was not related to the slope of the relationship between phylogenetic
  distance and interaction partner overlap. This suggests that 
  conservation of interaction partners among closely related plants
  (e.g., congeners or members of the same subfamilies) is more
  important than phylogenetic signal from deeper within the phylognetic
  tree. This echoes earlier results relating plant phylogeny to 
  predation by particular insect species~\citep{Novotny2002,Novotny2004,
  Odegaard2005} and in whole herbivory networks~\citep{Volf2017}. As
  we did not find any relationship between the families present in
  a network and the relationship between phylogenetic distance and
  interaction partner overlap in pollination or herbivory networks,
  the greater importance of shallow phylogeny (as reported for leaf
  miners and gallers in~\citet{Volf2017}) may be a general 
  feature of plant-insect interaction networks.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
    \end{center}
     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network. Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks. The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines. For both network types, the slopes obtained from permuted networks were always very close to 0.}
    \label{obs_vs_random} 
  \end{figure}

>>>>

  We found that the composition of plant families in a network
  was not related to the slope of the relationship between phylogenetic
  distance and interaction partner overlap. This suggests that 
  conservation of interaction partners among closely related plants
  (e.g., congeners or members of the same subfamilies) is more
  important than phylogenetic signal from deeper within the phylogenetic
  tree. This echoes earlier results relating plant phylogeny to 
  predation by particular insect species~\citep{Novotny2002,Novotny2004,
  Odegaard2005} and in whole herbivory networks~\citep{Volf2017}. As
  we did not find any relationship between the families present in
  a network and the relationship between phylogenetic distance and
  interaction partner overlap in pollination or herbivory networks,
  the greater importance of shallow phylogeny (as reported for leaf
  miners and gallers in~\citet{Volf2017}) may be a general 
  feature of plant-insect interaction networks.

@@

  \begin{figure}[!h]
    \begin{center}
      \centerline{\includegraphics*[height=.75\textwidth]{Figures/dataplots/observed_vs_random.eps}}
    \end{center}
     \caption{The slopes of the mixed-effect logistic regression of pairwise niche overlap against phylogenetic distance was signficantly different from 0 for each network. Here we show the observed slopes for herbivory (green squares) and pollination (purple diamonds) networks. Thick, dashed lines represent the mean slopes across all networks of each type. The maximum and minimum slopes obtained from 999 permutations of each network are depicted by thin, black lines. For both network types, the slopes obtained from permuted networks were always very close to 0.}
    \label{obs_vs_random} 
  \end{figure}
